Random Forests", OAs

### 2025-02-08 src/la_RF.Rmd
oa

library(tidyverse)
library(rprojroot)
library(rgdal)
library(rgeos)
library(sf)
library(spdep)
#library(tmap)
#library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)
#library(foreach)
library(doParallel)
library(raster)
library(plm)
#library(lmtest)
library(caret)
library(randomForest)
library(CAST)

@@

start.time <- Sys.time()
model.all <- train(n ~                                                          # REPLACE n WITH growth
                     #area + dist + dist.retail + London + south + n.slag + n.lag + n.l.slag + London.n.lag + n.nearest.city + year,
                     #I(n.London.lag/dist) + I(n.nearest.city.lag/London) + n.l.slag + year,
                     n.London.lag + n.nearest.city.lag + n.l.slag + year + London + dist, #n.nearest.retail.lag + dist.retail,
                   data = df,# %>% filter(year > 1999),                         # FILTER BY YEAR FOR GROWTH
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity")

@@

# [reproducible results]
# Random Forest 
# 
# 5984 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 5055, 4690, 4732, 5070, 5040, 4718, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE        Rsquared   MAE       
#   2     variance    0.03227897  0.8023185  0.01991724
#   2     extratrees  0.03150004  0.8057960  0.01912348
#   4     variance    0.03271887  0.7985855  0.02025685
#   4     extratrees  0.03174791  0.8047090  0.01932473
#   6     variance    0.03358260  0.7879953  0.02080616
#   6     extratrees  0.03207532  0.8018495  0.01964516
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = extratrees and min.node.size = 5.

@@

>>>>

library(tidyverse)
library(rprojroot)
# library(rgdal)
# library(rgeos)
# library(sf)
library(spdep)
#library(tmap)
#library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)
#library(foreach)
library(doParallel)
library(raster)
library(plm)
#library(lmtest)
library(caret)
library(randomForest)
library(CAST)

@@

# detectCores()
# cl <- makePSOCKcluster(14)
# registerDoParallel(cl)

start.time <- Sys.time()
model.all <- train(n ~                                                          # REPLACE n WITH growth
                     #area + dist + dist.retail + London + south + n.slag + n.lag + n.l.slag + London.n.lag + n.nearest.city + year,
                     #I(n.London.lag/dist) + I(n.nearest.city.lag/London) + n.l.slag + year,
                     n.London.lag + n.nearest.city.lag + n.l.slag + year + London + dist, #n.nearest.retail.lag + dist.retail,
                   data = df,# %>% filter(year > 1999),                         # FILTER BY YEAR FOR GROWTH
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity",
                   num.threads = 15)

# stopCluster(cl)
end.time <- Sys.time()
time.taken <- round(end.time - start.time,2)
time.taken

@@

# [reproducible results]
# Random Forest 
# 
# 5984 samples
#    6 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 5082, 4354, 4650, 4746, 5130, 4928, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE        Rsquared   MAE       
#   2     variance    0.03216513  0.7810704  0.02077849
#   2     extratrees  0.03220664  0.7752043  0.02087374
#   4     variance    0.03271488  0.7775723  0.02134707
#   4     extratrees  0.03229937  0.7760603  0.02102094
#   6     variance    0.03397678  0.7680207  0.02235307
#   6     extratrees  0.03248101  0.7767931  0.02132943
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 2, splitrule = variance
#  and min.node.size = 5.

@@

### FROM NOW ON, IT HAS NOT BEEN USED FOR SUBMISSION 2

### 2025-02-08 src/oa_RF_corrected.Rmd
oa

# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 3215700, 2574600, 3128916, 3225315, 2789175, 2618196, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE     
#   2     variance    3.235219  0.3131576  1.211443
#   2     extratrees  3.452069  0.2176445  1.182582
#   5     variance    3.217974  0.3337214  1.233777
#   5     extratrees  3.386142  0.2500448  1.251388
#   8     variance    3.294155  0.3208588  1.240884
#   8     extratrees  3.418390  0.2496608  1.281916
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 5, splitrule
#  = variance and min.node.size = 5.

>>>>

# [not reproducible despite having the code as the LAD models]
# Random Forest 
# 
# 3716736 samples
#       8 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 3215700, 2574600, 3128916, 3225315, 2789175, 2618196, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE     
#   2     variance    3.236301  0.3128048  1.211779
#   2     extratrees  3.453903  0.2169766  1.184256
#   5     variance    3.217652  0.3331498  1.233429
#   5     extratrees  3.390341  0.2491582  1.254907
#   8     variance    3.296126  0.3199896  1.241124
#   8     extratrees  3.418875  0.2485125  1.283134
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 5, splitrule = variance
#  and min.node.size = 5.
